---
title: "Artificial Data Analysis"
author: "Florian Stijven"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
    number_sections: true
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 10)
# Load packages
library(DynTxRegime)
library(tidyverse)
library(sas7bdat)
# Specify file locations.
OTR_vs_file_1 = "OTR analyses/OTR-estimation/VSC/results/OTR_artificial_results_cesd.rds"
OTR_q_file = "OTR analyses/OTR-estimation/OTR_q_results_update.rds"
```

```{r}
# Function to standardize vector to unit norm.
norm_vec = function(vec) {
  # Normalize the vector
  normed_vec = vec / sqrt(sum(vec * vec))
  return(normed_vec)
}
```

```{r}
# Source file that contains functions to estimate the value of a given regime 
# using the AIPW estimator, and the corresponding SE.
source(file = "OTR analyses/value_AIPW.R")
source(file = "OTR analyses/swv_ML.R")
source(file = "OTR analyses/swv_OLS.R")
source(file = "OTR analyses/value_AIPW_swv.R")
source(file = "OTR analyses/value_AIPW_se.R")
# Function to estimate the value of a regime based on the AIPW estimator. We 
# need this additional function because the DynTxRegime package does not provide
# function to estimate the value of regimes, estimated by Q-learning, with the
# AIPW estimator. 
value_regime_aipwe = function(regime, regime_allocation = optTx(regime)$optimalTx, se = TRUE) {
  # formula for the outcome regression model.
  OR_formula = regime@analysis@outcome@modelObj@model
  # Propensity score model.
  moPS <- modelObj::buildModelObj(
    model = ~ 1,
    solver.method = 'glm',
    solver.args = list(family = 'binomial'),
    predict.method = 'predict.glm',
    predict.args = list(type = 'response')
  )
  # Outcome regression model.
  moOR <- modelObj::buildModelObj(
    model = OR_formula,
    solver.method = 'lm',
    predict.method = 'predict.lm'
  )
  # The imputed data set is extracted from the qlearning object.
  data = regime@analysis@outcome@fitObj[["model"]]
  # The outcome is extracted.
  outcome = data$YinternalY
  data = data[, -1]
  # Return the estimated value.
  if (se) {
    value = value_AIPW_se(
      moOR = moOR,
      moPS = moPS,
      data = data,
      y = outcome,
      txName = "group_int",
      regime = regime_allocation
    )
  }
  else {
    value = value_AIPW(
      moOR = moOR,
      moPS = moPS,
      data = data,
      y = outcome,
      txName = "group_int",
      regime = regime_allocation
    )
  }

}
```



```{r}
# Load tibble that contains the estimated treatment regimes for the value search
# estimator.
OTR_value_search_tbl = 
  bind_rows(
    # Regimes estimated for update 1 data.
    readRDS(OTR_vs_file_1) %>%
      filter(update == 1L) %>%
      mutate(outcome_model = "Correct")
    ) %>%
      rename(regime = OTR_estimated) %>%
      mutate(estimated_value = sapply(X = regime,
                                      FUN = estimator)) %>%
      # Among the multiple runs, we select the run that has the largest estimated
      # value.
      group_by(X_Imputation_, outcome, imputation, update, outcome_model) %>%
      slice_max(order_by = estimated_value,
                n = 1,
                with_ties = FALSE) %>%
      ungroup() %>%
      select(-seed) %>%
      mutate(
        regime_parameters = lapply(
          X = regime,
          FUN = function(x)
            norm_vec(regimeCoef(x))
        ),
        optTx = lapply(
          X = regime,
          FUN = function(x)
            optTx(x)[[1]]
        )
      ) %>%
      mutate(
        constant = t(as.data.frame(regime_parameters))[, 1],
        sex = t(as.data.frame(regime_parameters))[, 2],
        age = t(as.data.frame(regime_parameters))[, 3],
        famfun = t(as.data.frame(regime_parameters))[, 4],
        cesd = t(as.data.frame(regime_parameters))[, 5],
        past_MDD = t(as.data.frame(regime_parameters))[, 6]
      ) %>%
      select(-regime_parameters, -regime)

# Load tibble that contains the estimated treatment regimes for Q-learning.
OTR_q_tbl = readRDS(file = OTR_q_file) %>%
  ungroup()
OTR_q_tbl = OTR_q_tbl %>%
  mutate(
    estimated_value = sapply(
      X = regime,
      FUN = function(x)
        value_regime_aipwe(x, se = FALSE)$valueHat
    ),
    regime_parameters = lapply(
      X = regime,
      FUN = function(x)
        coef(x)$outcome$Combined[c(
          "group_int",
          "sexFemale:group_int",
          "age:group_int",
          "famfun:group_int",
          "cesd:group_int",
          "past_MDDYes:group_int"
        )]
    ),
    optTx = lapply(
      X = regime,
      FUN = function(x)
        optTx(x)[[1]]
    )
  ) %>%
  mutate(
    constant = t(as.data.frame(regime_parameters))[, 1],
    sex = t(as.data.frame(regime_parameters))[, 2],
    age = t(as.data.frame(regime_parameters))[, 3],
    famfun = t(as.data.frame(regime_parameters))[, 4],
    cesd = t(as.data.frame(regime_parameters))[, 5],
    past_MDD = t(as.data.frame(regime_parameters))[, 6]
  ) %>%
  select(-regime_parameters,-regime)
```

```{r, results='hide'}
# The results for value search estimation with the multi-run approach  and
# Q-learning are joined together in a single tibble.
OTR_results = bind_rows(
  OTR_value_search_tbl %>%
    mutate(OTR_method = "value search"),
  OTR_q_tbl %>%
    mutate(OTR_method = "Q-learning") %>%
  # We will further only look at CESD as outcome.
  filter(outcome == "cesd")
) 
# The original tibbles are removed to clear up space. 
# rm("OTR_value_search_tbl", "OTR_q_tbl")
head(OTR_results)
```

```{r}
# We again load the tibble that contains the estimated regimes by Q-learning.
# This helps us to applying the aggregated regimes to the imputed data sets
# without having to write much additional code.
OTR_q_tbl = readRDS(file = OTR_q_file) %>%
  ungroup() %>%
  # We will further only look at CESD as outcome.
  filter(outcome == "cesd")
```

```{r}
# Function that implement the circular mean.
circular_mean = function(x) {
  # Get column names from x. These are used further on.
  colnames_x = colnames(x)
  # Ensure that the rows have a unit norm. This should be satisfied beforehand.
  x = t(apply(as.matrix(x), MARGIN = 1, FUN = norm_vec))
  
  # Compute the columnwise mean.
  mean_vector = apply(x, MARGIN = 2, FUN = mean)
  # Convert the vector of means to a vector on the unit circle. This vector is
  # put into a row of a data frame.
  circular_mean_row = as.data.frame(t(data.frame(norm_vec(mean_vector))))
  # Rename columns according to the original column names of x.
  colnames(circular_mean_row) = colnames_x
  return(circular_mean_row)
}
```

```{r}
# Aggregate estimated treatment regimes using the circular mean.
circular_mean_aggregated = OTR_results %>%
  group_by(imputation, OTR_method, update, outcome_model) %>%
  reframe(
    data.frame(constant, sex, age, famfun, cesd, past_MDD) %>%
      circular_mean(),
    param_vector = data.frame(constant, sex, age, famfun, cesd, past_MDD) %>%
      circular_mean() %>%
      as.numeric() %>%
      list()
  ) 
```

```{r}
# Include the one-size-fits-all regimes. 
trivial_rules_tbl = expand_grid(
  imputation = c("Per Arm", "Global"),
  OTR_method = c("One-Size-Fits-All (0)", "One-Size-Fits-All (1)"),
  update = 1:2
)
trivial_rules_tbl = trivial_rules_tbl %>%
  left_join(
    tibble(
      OTR_method = c("One-Size-Fits-All (0)", "One-Size-Fits-All (1)"),
      regime_function = list(
        function(x) return(rep(0L, nrow(x))),
        function(x) return(rep(1L, nrow(x)))
      )
    )
  )
```


```{r}
# Combine different results of different aggregation methods into a single
# tibble. We cannot yet include the tibble that contains the majority votes
# regimes because the corresponding data handling is different.
aggregated_rules_tbl =
  circular_mean_aggregated %>%
  mutate(aggregation = "Circular Mean")
```

```{r, cache=TRUE}
# Add the aggregated treatment regimes as a function to the tibble.
aggregated_rules_tbl = aggregated_rules_tbl %>%
  mutate(regime_function = lapply(
    X = param_vector,
    FUN = function(param_vector) {
      function(covariates_matrix) {
        allocation = covariates_matrix %*% param_vector > 0
        return(as.integer(allocation))
      }
    }
  ))

aggregated_rules_tbl = bind_rows(
  aggregated_rules_tbl, 
  trivial_rules_tbl %>%
    mutate(aggregation = "One-Size-Fits-All", 
           outcome_model = "Correct")
)


# Apply aggregated regimes to the imputed data sets.
cont_formula = formula(~sex + age + famfun + cesd + past_MDD)
estimated_value_tbl = OTR_q_tbl %>%
  left_join(
    aggregated_rules_tbl %>%
      select(
        imputation,
        regime_function,
        OTR_method,
        aggregation,
        update,
        outcome_model
      )
  ) %>%
  mutate(allocation = purrr::map2(
    .x = regime,
    .y = regime_function,
    .f = function(regime, regime_function) {
      # Extract imputed data set
      data = regime@analysis@outcome@fitObj[["model"]]
      # Extract columns we need in the correct order.
      data = data[, c("sex", "age", "famfun", "cesd", "past_MDD")]
      data = model.matrix(cont_formula, data)
      regime_function(data)
    }
  )) %>%
  mutate(estimated_value_list = purrr::map2(
    .x = regime,
    .y = allocation,
    .f = function(regime, allocation) {
      value_regime_aipwe(regime, allocation)
    }
  )) %>%
  mutate(
    estimated_value = purrr::map_dbl(estimated_value_list, "valueHat"),
    estimated_value_se = purrr::map_dbl(estimated_value_list, "sigmaHat")
  ) %>%
  select(-regime, -regime_function, -allocation, -estimated_value_list)
```

```{r}
# Apply Rubin's rules
pooled_inference_aggregated_rules_tbl = estimated_value_tbl %>%
  group_by(imputation, OTR_method, aggregation, update, outcome_model) %>%
  summarise(
    pooled_estimated_value = mean(estimated_value),
    pooled_within_variance = mean(estimated_value_se ** 2),
    pooled_between_variance = var(estimated_value)
  ) %>%
  ungroup() %>%
  mutate(pooled_total_variance = pooled_within_variance + (1 + (1 / 40)) * pooled_between_variance)
```

In this document, we examine the influence of the imputation model, i.e., global
imputation versus imputation per arm, on the estimation of optimal treatment
regimes in the *modified Browne data*. The imputation per arm is a
*proper* imputation while global imputation is improper.

The *modified Browne data* are the Browne data where we artificially induce
relationships between baseline covariates and the outcome variable. In what
follows, we will only consider the CESD outcome measured at 6 months after
randomization (denoted by $\texttt{cesd2}$). For estimating the optimal regimes, 
we still consider the change scores, however. 
In the following bullet point, a tilde indicates the updated value for CESD at 6
months. Treatment $0$ is "Sertraline alone" and treatment $1$ is "Sertraline and
IPT".

* **Update 1.**  The outcome value is modified as follows,
$$\tilde{\texttt{cesd2}} = \texttt{cesd2} - (0.30 \cdot (\texttt{cesd} - 40) - 6 \cdot \texttt{past_MDD}) \cdot I(\texttt{group} = 1) + 0.20 \cdot (\texttt{cesd} - 40) + 4 \cdot \texttt{past_MDD}. $$
This update changes the interaction effects. Patients will thus benefit
more from the addition of IPT to Sertraline if they have a more severe
depression at baseline (larger baseline CESD and past MDD).

In the following analyses, we will only consider 40 imputations instead of the
200 imputations used for analyzing the original Browne data. This limits the 
computational burden. The *per arm* and *global* imputation models are the same
as for the analyses of the original Browne data.


# Choice of Imputation Model

In this section, we look at the influence of the imputation model on the
estimation of regimes by Q-learning and value search estimation. We only look at
the update 1 data.

## Estimated Values of Estimated Regimes

In the following histograms, the estimated values of the estimated regimes are
summarized across the 40 imputations. These histograms show that imputation per 
arm leads to larger estimated values.

```{r, fig.cap="Frequency distribution of the estimated values of the estimated regimes across the imputations for the update 1 data. Note that each histogram represents 40 estimated values of 40, possibly different, estimated regimes. The value is estimated by the AIPW estimator which is explained at the end of the document for the original Browne data."}
OTR_results %>%
  filter(update == 1L) %>%
  ggplot(aes(x = estimated_value)) +
  geom_histogram(color = "black", fill = "gray") +
  geom_vline(
    data = estimated_value_tbl %>%
      filter(aggregation == "One-Size-Fits-All", update == 1) %>%
      group_by(outcome, imputation, OTR_method) %>%
      summarise(pooled_estimated_value = mean(estimated_value)) %>%
      rename("Value of Trivial Regimes" = OTR_method),
    mapping = aes(xintercept = pooled_estimated_value, color = `Value of Trivial Regimes`)
  )  +
  xlab("Estimated Value") +
  ylab("Frequency") +
  scale_color_discrete(name = "Value of Trivial Regimes") +
  facet_grid(imputation ~ OTR_method)
```

The following table summarizes the above results. This confirms our previous
conclusions. 

```{r}
OTR_results %>%
  filter(update == 1L) %>%
  group_by(imputation, OTR_method) %>%
  summarise("Mean Estimated Value" = mean(estimated_value),
            "Between Imputation SD" = sd(estimated_value)) %>%
  arrange(OTR_method) %>%
  knitr::kable(digits = 3, 
               caption = "Average estimated value of the estimated regimes across the imputed data sets and the corresponding standard deviation. Note that each value is the average of 40 estimated values of 40, possibly different, estimated regimes. The value is estimated by the AIPW estimator which is explained at the end of the document for the original Browne data.")
```

## Distance from One-Size-Fits-All of Estimated Regimes

In the following figure and table, the same estimated regimes as above are summarized
by the corresponding $d = \min(p_1, p_2)$. This value measures the distance of 
the estimated regimes from a one-size-fits-all regime. The corresponding average
distances are summarized in the following table. 

For Q-learning, estimated regimes under imputation per arm tend to be further 
away from one-size-fits-all. However, there is no considerable difference for
the regimes estimated by value search estimation.

```{r, fig.cap="Frequency distribution of the distance from one-size-fits-all for the estimated regimes across the imputations."}
OTR_results %>%
  filter(update == 1) %>%
    mutate(d = sapply(
    X = optTx, 
    FUN = function(x) {
      p = mean(x)
      return(min(c(p, 1 - p)))
    }
  )) %>%
  ggplot(aes(x = d))+
  geom_histogram(color = "black", fill = "gray") +
  xlim(c(0.3, 0.5)) +
  xlab("Distance from One-Size-Fits-All regime (d)") +
  ylab("Frequency") +
  facet_grid(imputation~OTR_method)
```


```{r}
OTR_results %>%
  filter(update == 1) %>%
    mutate(d = sapply(
    X = optTx, 
    FUN = function(x) {
      p = mean(x)
      return(min(c(p, 1 - p)))
    }
  )) %>%
  group_by(imputation, OTR_method) %>%
  summarise(mean_d = mean(d)) %>%
  tidyr::pivot_wider(values_from = "mean_d", names_from = "imputation") %>%
  knitr::kable(digits = 3,
               caption = "Average distance from one-size-fits-all of the estimated regimes across the imputed data sets. Note that each value is the average of 40 distances of 40, possibly different, estimated regimes.")
```

## Aggregated Regimes

Finally, we aggregate the 40 estimated regimes in each setting (imputation and
regime estimation method) with the circular mean. We consider the pooled
estimate of the value and the corresponding 95% CIs in the following figure and
table (by applying Rubin's rules). The results for the trivial regimes are added
for reference.

The figure below confirms the previous results. Imputation per arm leads to a
better aggregated regime in terms of the pooled estimate of its value. This
holds for both Q-learning and value search estimation. Even though this
difference is likely of little clinical relevance, it is still a considerable
difference when taking into account that only about 10% of the patients have
missing values (at 6 months).


```{r, fig.cap="Pooled estimates for the value of the aggregated regimes together with 95% confidence intervals for the update 1 data. The pooled estimates and confidence interval are obtained by applying Rubin's rules."}
pooled_inference_aggregated_rules_tbl %>%
  filter(update == 1L, aggregation %in% c("Circular Mean", "One-Size-Fits-All")) %>%
  ggplot(aes(y = OTR_method, x = pooled_estimated_value, color = imputation)) +
  geom_point(aes(fill = imputation), position = position_dodge(width = .3)) +
    geom_errorbarh(
    aes(
      xmin = pooled_estimated_value - 1.96 * sqrt(pooled_total_variance),
      xmax = pooled_estimated_value + 1.96 * sqrt(pooled_total_variance)
    ),
    height = 0.2,
    position = position_dodge(width = .3),
  ) +
  xlab("Pooled Estimated Value") +
  ylab("Estimation Method") +
  scale_color_discrete(name = "OTR method") +
  scale_fill_discrete(name = "OTR method") +
  ggtitle("Estimated Value with 95% CI")
```

```{r}
pooled_inference_aggregated_rules_tbl %>%
  filter(update == 1L,
         aggregation %in% c("Circular Mean", "One-Size-Fits-All")) %>%
  mutate(
    "ll 95% CI" = pooled_estimated_value - 1.96 * sqrt(pooled_total_variance),
    "ul 95% CI" = pooled_estimated_value + 1.96 * sqrt(pooled_total_variance)
  ) %>%
  select(imputation,
         OTR_method,
         pooled_estimated_value,
         "ll 95% CI",
         "ul 95% CI") %>%
  knitr::kable(digits = 3, 
               caption = "Pooled estimated values for the aggregated regimes. Inference is based on the application of Rubin's rules.")
```


In the next table, the aggregated regime parameters are summarized. The
estimated parameters for CESD and past MDD tend to be closer to zero under
global imputation. Although the difference in estimated parameters is relatively
small, there is a considerable difference in the corresponding pooled estimated
value (as was shown above).

```{r}
interpretation_tbl = aggregated_rules_tbl %>%
  filter(update == 1, OTR_method %in% c("Q-learning", "value search")) %>%
  # For Q-learning, the regime is aggregated with Rubin's rules. Therefore, the
  # aggregated regime's parameter vector will not have the unit norm. To ease
  # comparison of parameters, we convert these parameter vectors to unit norm.
  mutate(norm = sapply(
    X = param_vector,
    FUN = function(param_vector)
      sqrt(sum(param_vector * param_vector))
  )) %>%
  # Divide the regime parameters by the norm. 
  mutate(constant = constant / norm,
         sex = sex / norm,
         age = age / norm,
         famfun = famfun / norm,
         cesd = cesd / norm,
         past_MDD = past_MDD / norm) %>%
  select(c(1:2, 4:9)) %>%
  arrange(OTR_method)
# Add variable names with information on the dummy coding.
# colnames(interpretation_tbl)[3:8] = covariate_coding_names
interpretation_tbl %>%
  knitr::kable(digits = 3,
               caption = "Linear regime parameter estimates for the aggregated regimes (without additional modificiations) for the update 1 data. The respective parameter vectors have unit norm.")
```



