---
title: "Modified Browne Data - Motivation for Modifications"
author: "Florian Stijven"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    df_print: paged
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    number_sections: yes
  word_document:
    toc: yes
    number_sections: yes
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 10)
library(tidyverse)
library(sas7bdat)
```


```{r}
# Read the Browne data.
original_data = read.sas7bdat(file = "data preparation and exploration/final.sas7bdat")

# Recode NaN values to the approriate NA values. For some reason, missing values
# in a sas data set are not recognized as NA's in R.
original_data = original_data %>%
  mutate(across(.cols = everything(), .fns = function(x) ifelse(is.nan(x), NA, x)))

# Recode the group, sex, and disorder variables into a factor variables.
original_data = original_data %>%
  mutate(group = factor(
    group,
    labels = c("Sertraline alone", "Sertraline and IPT", "IPT"),
    levels = 1:3
  ),
  sex = factor(
    sex,
    labels = c("Male", "Female"),
    levels = 1:2
  ),
  disorder = factor(
    disorder,
    labels = c("Never", "Past", "Current", "Current and Past"),
    levels = 1:4
  ))

# Recode disorder variable into two binary variables.
original_data = original_data %>%
  mutate(
    past_MDD = fct_collapse(
      .f = disorder,
      "No" = c("Never", "Current"),
      "Yes" = c("Past", "Current and Past")
    ),
    current_MDD = fct_collapse(
      .f = disorder,
      "No" = c("Never", "Past"),
      "Yes" = c("Current", "Current and Past")
    )
  )

# Change variable names to improve consistency.
original_data = original_data %>%
  rename(madrs = madrsv1, madrs2 = madrst2,
         sas = sasb, sas2 = sasb2)

# Remove outcomes measured after six months. 
original_data = original_data %>%
  select(-cesd3, -cesd4, -famfun3, -famfun4,
         -madrst3, -madrst4, -vas3, -vas4,
         -sasb3, -sasb4)

# Add change score for CESD as outcome and remove the "IPT" treatment group . 
original_data = original_data %>%
  mutate(change_cesd = cesd - cesd2) %>%
  filter(group != "IPT")

```

In this document, we justify the choices to add additional effects of covariates
on the outcomes in the original Browne data. We only consider CESD at 6 months as
outcome. These additional effects are artificially added to illustrate some
ideas that cannot be illustrated with the original data because these
(interaction) effects are not present there. We consider the following artificial data
set.

* We add a treatment-interaction effect for past major depressive disorder
(MDD) (`past_MDD`) and baseline CESD (`cesd`) for their effect on CESD at 6
months (`cesd2`). So, these two baseline covariates are artificially turned into
treatment effect modifiers.

We first give some results and plots for the original data where we do an
available case analysis to deal with the missing data. This provides a reference
to compare the "updated" data sets with. The goal is to change the original data
in such a way that the artificial data are still plausible. 

```{r}
# Define formula for two regression models that will be used further on.
global_formula = formula(change_cesd ~ group + sex + age + past_MDD + numchild + phealth + madrs + sas + famfun + cesd + vas)
per_arm_formula = update(global_formula, ~.*group)

```


# Original data


The outcome regression model for change in CESD is fitted with and without all
interaction terms with treatment. These estimated models are summarized next.
The values between brackets are the estimated standard errors.

```{r}
lm_fit0_global = lm(global_formula, original_data)
lm_fit0_per_arm = lm(per_arm_formula, original_data)
modelsummary::msummary(
  list("No Interactions" = lm_fit0_global,
       "Treatment-Interactions" = lm_fit0_per_arm),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  notes = "+, p < 0.1; *, p < 0.05; **, p < 0.01; ***, p < 0.001.",
  gof_map = c("r.squared", "adj.r.squared")
)
```

We next plot the change score against baseline CESD, stratified by treatment and
past MDD. Smooth fits are added to facilitate the interpretation. The gray
shaded regions are 95% confidence intervals around the smooth curves. 

```{r}
original_data %>%
  ggplot(aes(x = cesd, y = change_cesd, color = group, linetype = past_MDD)) +
  geom_point(alpha = 0.4) + 
  geom_smooth(se = TRUE) +
  ylab("Change in CESD (baseline - 6 months)") +
  xlab("Baseline CESD")
```


# Update 1

The (first) update involves the introduction of additional treatment effect
heterogeneity. The modification of the outcome variable is as follows,
$$\tilde{\texttt{cesd2}} = \texttt{cesd2} - (0.30 \cdot (\texttt{cesd} - 40) - 6 \cdot \texttt{past_MDD}) \cdot I(\texttt{group} = 1) + 0.20 \cdot (\texttt{cesd} - 40) + 4 \cdot \texttt{past_MDD}$$
where a tilde indicates the updated value and group $1$ corresponds to
"Sertraline and IPT". Patients will thus benefit more "Sertraline and IPT" (as
compared to "Sertraline alone") if they have a more severe depression at
baseline (larger CESD and past MDD).


```{r}
data_update1 = original_data %>%
  filter(group != "IPT") %>%
  mutate(
    cesd2 = ifelse(
      group == "Sertraline and IPT",
      cesd2 - 0.30 * (cesd - 40) - 6 * (past_MDD == "Yes")              ,
      cesd2
    ),
    cesd2 = cesd2 + 0.20 * (cesd - 40) + 4 * (past_MDD == "Yes"),
    change_cesd = cesd - cesd2
  )
```


We next repeat the same regression models and plots as before. There now is 
a signficant interaction effect for past MDD and baseline CESD. Note also that
there is a slight change in R-squared.

```{r}
lm_fit1_global = lm(global_formula, data_update1)
lm_fit1_per_arm = lm(per_arm_formula, data_update1)
modelsummary::msummary(
  list("No Interactions" = lm_fit1_global,
       "Treatment-Interactions" = lm_fit1_per_arm),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  notes = "+, p < 0.1; *, p < 0.05; **, p < 0.01; ***, p < 0.001.",
  gof_map = c("r.squared", "adj.r.squared")
)
```

The following plot is the same as for the original data, but the plot now 
suggests some degree of treatment effect heterogeneity. 

```{r}
data_update1 %>%
  ggplot(aes(x = cesd, y = change_cesd, color = group, linetype = past_MDD)) +
  geom_point(alpha = 0.4) + 
  geom_smooth(se = TRUE) +
  ylab("Change in CESD (baseline - 6 months)") +
  xlab("Baseline CESD")
```

